% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yang Cheng}

\basicInfo{
  \email{newplan001@163.com} \textperiodcentered\ 
  \phone{(+86) 1XX-XXX-XXX6} \textperiodcentered\ 
  \homepage[https://chengyang.info]{https://chengyang.info}}

%\section{\faGraduationCap\ Education}
\section{Education}
\datedsubsection{\textbf{Tsinghua University}, Beijng, China}{2016.09 -- Present}
\textit{Ph.D. student} in Computer Science and Technology\\
Advisor(s): Prof. Jianping Wu and Asoc. Prof. Dan Li\\
Research Interest: Distributed System, Networking Optimization, and System Security
\datedsubsection{\textbf{University of Electronic Science and Technology of China}, Chengdu, China}{2012.09 -- 2016.07}
\textit{B.Eng.} in Software Engineering\\
GPA/Ranking: 3.8/4.0,  \nth{1}/103

%\section{\faUsers\ Working Experience}
\section{Working Experience}
\datedsubsection{\textbf{Microsoft Research Asia}, Research Intern}{2018.04 -- 2018.10}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Leading the AIPre project to accelerate end-to-end DL workflow in the cloud.
  %\item Explored the efficiency of deep learning systems from an end-to-end perspective;
  %\item Optimized DL frameworks to achieve maximum GPU performance in end2end DL workflows.
\end{itemize}

\datedsubsection{\textbf{Chengdu Haocaiduo Agricultural Technology Co. Ltd.}, Developing Engineer}{2014.06 -- 2014.07}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Developing intelligent agricultural management system to simplify the management of crops;
	%\item Developed communication primitives for agricultural sensors based on the ZigBee protocol.
\end{itemize}

\datedsubsection{\textbf{Tsinghua University}, Teaching Assistant}{}
\begin{itemize}
	\item \datedline{[00240112-90], [undergraduates], Next Generation Internet}{Spring of 2019}
	\item \datedline{[00240112-90], [undergraduates], Next Generation Internet}{Spring of 2018}	
	\item \datedline{[74120023-0], [graduates], Security Foundation and Frontier of Cyberspace}{Autumn of 2017}
\end{itemize}


%\section{\faUsers\ Working Experience}
\section{Selected Projects}
\datedsubsection{AIPre: Boosting end-to-end DL eorkflows in the cloud}{2018.04 -- 2018.10}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Evaluate the performance of deep learning systems widely used today, from an end-to-end perspective;
	\item Offload data preprocessing workloads to FPGAs to remove the CPU bottleneck in end2end DL workflows;
	\item Overlap computation and communication by re-scheduling the computation workflow in BP;
\end{itemize}

\datedsubsection{BML: A scalable and high-performance DML system}{2017.09 -- 2018.01}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Design novel synchronization paradigms for distributed Tensorflow, reducing data to be synchronized;
	\item Incorporate RDMA and BCube topology to achieve high-performance data communication primitives;
	\item Outperform the PS paradigm and the Ring paradigm by up to 2.4$\times$ and 1.2$\times$, respectively.
\end{itemize}

\datedsubsection{Virtual desktop management and control system}{2015.01 -- 2015.08}
\begin{itemize}
	\item Design a high-performance, cross-platform virtual desktop management system, with the SPICE protocol;
	\item Implement tin-clients for Android and PC platform respectively,  to and interact with remote VM servers;
	\item Design and implement SMx(2/3/4)-based encryption mechanism to protect user information from leakage
\end{itemize}


\section{Publications}
\datedsubsection{DLBooster: Boosting End-to-End Deep Learning Workflows with Offloading Data Preprocessing Pipelines}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item \textbf{Yang Cheng}, Dan Li, Zhiyuan Guo, Binyao Jiang, Jiaxin Lin, Xi Fan, Jinkun Geng, Xinyi Yu, Wei Bai, Lei Qu, Ran Shu, Peng Cheng, Yongqiang Xiong, Jianping Wu
	\item \textit{48th International Conference on Parallel Processing (ICPP 2019)}
\end{itemize}

\datedsubsection{Impact of Network Topology on the Performance of DML: Theoretical Analysis and Practical Factors}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Shuai Wang, Dan Li, Jinkun Geng, Yue Gu, and \textbf{Yang Cheng}
	\item \textit{IEEE International Conference on Computer Communications (INFOCOM 2019)}
\end{itemize}

\datedsubsection{BML: A High-performance, Low-cost Gradient Synchronization Algorithm for DML Training}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Songtao Wang, Dan Li, \textbf{Yang Cheng}, Jinkun Geng, Yanshu Wang, Shuai Wang, Shutao Xia, Jianping Wu
	\item \textit{Thirty-second Conference on Neural Information Processing Systems (NeurIPS 2018)}
\end{itemize}


\datedsubsection{Bridging machine learning and computer network research: a survey}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item \textbf{Yang Cheng}, Jinkun Geng, Yanshu Wang, Junfeng Li, Dan Li, Jianping Wu
	\item \textit{CCF Transactions on Networking (CCF ToN)}
\end{itemize}

\datedsubsection{Dante: Enabling FOV-Aware Adaptive FEC Coding for 360-Degree Video Streaming}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Zhetao Li, Fei Gui, Jinkun Geng, Dan Li, Zhibo Wang, Junfeng Li,\textbf{Yang Cheng}, Usama Zafar
	\item \textit{2nd Asia-Pacific Workshop on Networking (APNet 2018)}
\end{itemize}

\datedsubsection{HiPS: Hierarchical Parameter Synchronization in Large-Scale Distributed Machine Learning}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Jinkun Geng, Dan Li,\textbf{Yang Cheng},Shuai Wang, Junfeng Li
	\item \textit{ACM SIGCOMM 2018 Workshop on Network Meets AI \& ML (NetAI 2018)}
\end{itemize}

\datedsubsection{Quick NAT: High performance NAT system on commodity platforms}{}
%\role{Research Intern}{Manager(s): Yongqiang Xiong and Guangshu Liu}
%Brief introduction: xxx.
\begin{itemize}
	\item Junfeng Li, Dan Li, Yukai Huang, \textbf{Yang Cheng}, Ruilin Ling
	\item \textit{23th IEEE International Symposium on Local and Metropolitan Area Networks (LANMAN 2017)}
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\if false
%\section{\faCogs\ Skills}
\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}
\fi

%\section{\faHeartO\ Honors and Awards}
\section{Selected Honors}
\datedline{Outstanding graduates in Sichuan province}{Jun. 2016}
\datedline{Tang Lixin Scholarship, UESTC}{Sep. 2015}
\datedline{National Scholarship}{Sep. 2015}
\datedline{National Endeavor Scholarship}{Sep. 2013}
\datedline{First price, Award on the \nth{8} National College Student Information Security Contest}{Aug. 2015}
\datedline{First price, Award on the \nth{6} National College Students Mathematics Competition, Sichuan}{Nov. 2014}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
